### 2022-02-23 sections/strategy_Htautau.tex
update pt plots

@@

\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l2tau1bnj_os.pdf} &
\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b1j_ss.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b2j_ss.pdf}\\

@@

\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b2j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b3j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\

@@

\includegraphics[page=1,width=0.33\textwidth]{figures/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\

>>>>

%   \begin{table}
%   \centering
%   \caption{Overview of the signal regions and the control regions used for fake tau scale factor derivation in leptonic channels.}
%   \label{tab:srcr}
%   \begin{tabular}[h]{c|c|c|c|c|c|c}
%   \hline \hline
%   \multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
%   \multirow{7}{*}{SR}&$t_l\thadhad$     & 1     & any                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
%   &$t_l\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
%   &$t_l\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
%   &$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
%   &$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
%   &$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
%   &$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
%   \multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
%   &$t_lt_l2b\tauhad$      & 2     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
%   &$t_lt_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
%   &$t_lt_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ OS\\ \cline{2-7}
%   &$t_lt_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
%   &$t_lt_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_l\tauhad$ OS\\ \hline
%   \end{tabular}
%   \end{table}

@@

\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l2tau1bnj_os.pdf} &
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b1j_ss.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\

@@

\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\

@@

\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
